\bf\mftitle

### 2011-01-16 doc/jInfer/architecture/architecture.tex
Documentation: Capabilities

% TODO vektor Talk about Capabilities
\section{NetBeans Modules}

TODO vektor capabilities too
TODO vektor anti thinks, we should talk about properties windows and plugability of autoeditor, or thats part of some other developer doc?

>>>>

\subsection{Capabilities} \label{section_capabilities}
From time to time, modules need a flow of certain information in completely opposite way to the usual inference: they need to know what the following module can or cannot do.\\

For this reason, inference modules extend the \code{Capabilities} interface defining a single method: \code{getCapabilities()}. This method returns a list of strings representing the abilities, or "capabilities" of this module.\\

An inference module can query the capabilities of the \textit{next} module in the inference chain by invoking the \code{RunningProject.getNextModuleCaps()} method to obtain the next module encapsulated in the \code{Capabilities} interface.\\

At the moment, only one capability is defined to be communicated across modules, more specifically between \jmodule{IGGenerator} and \jmodule{Simplifier}. This is \code{Capabilities.CAN\_HANDLE\_COMPLEX\_REGEXPS} meaning whether the \code{Simplifier} accepts more complicated regular expressions than simple concatenations of tokens on its input.\\
% TODO vektor check later - didn't this change?!?

Example of Capabilities usage taken from \jmodule{XSDImporter} module:
\begin{verbatim}
  // if the next module cannot handle complex regexps, help it by expanding our result
  if (!RunningProject.getNextModuleCaps().getCapabilities()
               .contains(Capabilities.CAN_HANDLE_COMPLEX_REGEXPS)) { 
    // lookup expander
    final Expander expander = Lookup.getDefault().lookup(Expander.class);
    // return expanded
    return expander.expand(parser.getRules());
  }
  // return not expanded rules
  return parser.getRules();
\end{verbatim}

\section{NetBeans Modules}

% TODO vektor anti thinks, we should talk about properties windows and plugability of autoeditor, or thats part of some other developer doc?
% property windows, autoeditor and ruledisplayer will be handled in dev tutorial -- vektor
